Combining Object-Oriented Paradigm and Controlled Natural Language for Requirements Specification

### 2021-12-18 article.tex
links

\documentclass[sigplan,10pt,screen]{acmart}
% \settopmatter{printfolios=false,printccs=false,printacmref=false}
\usepackage[underline=true,rounded corners=false]{pgf-umlsd} % for UML sequence diagrams
\usepackage[square]{syntax} % for BNF grammar
  \setlength{\grammarparsep}{1pt}
  \setlength{\grammarindent}{2em}
\usepackage{array} % complex structure of TABULAR-s
\usepackage{paralist} % for inline itemized lists env{inparaenum}
\usepackage{natbib} % for customization of bibliography headers
\usepackage{ffcode}
\usepackage{flushend}
\usepackage{tikz}
  \usetikzlibrary{shapes,arrows,shadows}
  \usetikzlibrary{decorations.pathmorphing}
  \usetikzlibrary{positioning,fit}
  \usetikzlibrary{calc}

\newcommand{\nospell}[1]{#1}
\setlength\headheight{24pt}
\newcommand\figcaption[1]{\Description{#1}\caption{#1}}
\raggedbottom
\tolerance=2000

@@

\title{Combining Object-Oriented Paradigm and Controlled Natural Language for Requirements Specification}
\author{Yegor Bugayenko}
\orcid{0000-0001-6370-0678}
\email{yegor256@gmail.com}
\affiliation{\city{Moscow}\country{Russia}}

@@

It is an object-oriented CNL that resembles English and, because of that,
can be read and understood by compilers, system analysts, end-users, and
business people. Fig.~\ref{fig:example} presents an example of a short
requirements definition document that describes a calculator that asks its
user for two floating point numbers and returns the result of their
division.

@@

\subsection{Method calls match declarations}

@@

\subsection{Object creating have necessary constructor arguments}

@@

\subsection{Variable bindings precede their usage}

@@

\subsection{Methods return objects of required classes}

@@

\subsection{Failures are handled by alternative flows}

@@

\begin{table}
\begin{tabular}{>{\raggedright}p{14em}rrr}
                                            & $p_1$ & $p_2$ & $p_3$ \\
\hline
Total classes                                 & 39 & 12 & 19 \\
Total methods                                 & 19 & 7 & 24 \\
Total Java classes                                  & 80 & 75 & 295 \\
Ambiguity achieved                                  & 0.80 & 0.95 & 0.68 \\
Work spent on RE, staff-months                      & 0.53 & 0.21 & 0.86 \\
Total SRS contributors                              & 4 & 7 & 2 \\
Non-empty lines of Java code                        & 9.5K & 10K & 32K \\
Project duration, months                            & 7 & 26 & 11 \\
Project budget, staff-months                        & 5.5 & 7.5 & 9.5 \\
\hline
\end{tabular}
\figcaption{Empirically collected data from three commercial projects}
\label{table:numbers}
\end{table}

@@

\bibliographystyle{ACM-Reference-Format}
\raggedright
\bibliography{main}
\clearpage

>>>>

\documentclass[sigplan,screen]{acmart}
\usepackage[underline=true,rounded corners=false]{pgf-umlsd} % for UML sequence diagrams
\usepackage{array} % complex structure of TABULAR-s
\usepackage{paralist} % for inline itemized lists env{inparaenum}
\usepackage[nonumbers,noframes]{ffcode}
\usepackage{tikz}
  \usetikzlibrary{shapes,arrows,shadows}
  \usetikzlibrary{decorations.pathmorphing}
  \usetikzlibrary{positioning,fit}
  \usetikzlibrary{calc}

\newcommand{\nospell}[1]{#1}
\newcommand\figcaption[1]{\Description{#1}\caption{#1}}
% \tolerance=2000

@@

\title{Combining Object-Oriented Paradigm and Controlled Natural Language for Requirements Specification}
\author{Yegor Bugayenko}
\orcid{0000-0001-6370-0678}
\email{yegor256@gmail.com}
\affiliation{\institution{Huawei}\city{Moscow}\country{Russia}}

@@

Requs\footnote{\url{https://www.requs.org}}
is an object-oriented CNL that resembles English and, because of that,
can be read and understood by compilers, system analysts, end-users, and
business people. Fig.~\ref{fig:example} presents an example of a short
requirements definition document that describes a calculator that asks its
user for two floating point numbers and returns the result of their
division.

@@

\subsection{Method Calls Match Declarations}

@@

\subsection{Object Creating Have Necessary Constructor Arguments}

@@

\subsection{Variable Bindings Precede Their Usage}

@@

\subsection{Methods Return Objects of Required Classes}

@@

\subsection{Failures Are Handled by Alternative Flows}

@@

\begin{table}
\figcaption{Empirically collected data from three commercial projects}
\label{table:numbers}
\begin{tabular}{>{\raggedright}p{14em}rrr}
                                            & $p_1$ & $p_2$ & $p_3$ \\
\hline
Total classes                                 & 39 & 12 & 19 \\
Total methods                                 & 19 & 7 & 24 \\
Total Java classes                                  & 80 & 75 & 295 \\
Ambiguity achieved                                  & 0.80 & 0.95 & 0.68 \\
Work spent on RE, staff-months                      & 0.53 & 0.21 & 0.86 \\
Total SRS contributors                              & 4 & 7 & 2 \\
Non-empty lines of Java code                        & 9.5K & 10K & 32K \\
Project duration, months                            & 7 & 26 & 11 \\
Project budget, staff-months                        & 5.5 & 7.5 & 9.5 \\
\hline
\end{tabular}
\end{table}

@@

%%% -*-BibTeX-*-
%%% Do NOT edit. File created by BibTeX with style
%%% ACM-Reference-Format-Journals [18-Jan-2012].

\begin{thebibliography}{18}

%%% ====================================================================
%%% NOTE TO THE USER: you can override these defaults by providing
%%% customized versions of any of these macros before the \bibliography
%%% command.  Each of them MUST provide its own final punctuation,
%%% except for \shownote{}, \showDOI{}, and \showURL{}.  The latter two
%%% do not use final punctuation, in order to avoid confusing it with
%%% the Web address.
%%%
%%% To suppress output of a particular field, define its macro to expand
%%% to an empty string, or better, \unskip, like this:
%%%
%%% \newcommand{\showDOI}[1]{\unskip}   % LaTeX syntax
%%%
%%% \def \showDOI #1{\unskip}           % plain TeX syntax
%%%
%%% ====================================================================

\ifx \showCODEN    \undefined \def \showCODEN     #1{\unskip}     \fi
\ifx \showDOI      \undefined \def \showDOI       #1{#1}\fi
\ifx \showISBNx    \undefined \def \showISBNx     #1{\unskip}     \fi
\ifx \showISBNxiii \undefined \def \showISBNxiii  #1{\unskip}     \fi
\ifx \showISSN     \undefined \def \showISSN      #1{\unskip}     \fi
\ifx \showLCCN     \undefined \def \showLCCN      #1{\unskip}     \fi
\ifx \shownote     \undefined \def \shownote      #1{#1}          \fi
\ifx \showarticletitle \undefined \def \showarticletitle #1{#1}   \fi
\ifx \showURL      \undefined \def \showURL       {\relax}        \fi
% The following commands are used for tagged output and should be
% invisible to TeX
\providecommand\bibfield[2]{#2}
\providecommand\bibinfo[2]{#2}
\providecommand\natexlab[1]{#1}
\providecommand\showeprint[2][]{arXiv:#2}

\bibitem[\protect\citeauthoryear{??}{ste}{2005}]%
        {ste05}
 \bibinfo{year}{2005}\natexlab{}.
\newblock \bibinfo{booktitle}{\emph{ASD Simplified Technical English.
  International specification for the preparation of maintenance documentation
  in a controlled language}}.
\newblock Number Specification ASD-STE100. \bibinfo{publisher}{Simplified
  Technical English Maintenance Group (STEMG)}.
\newblock

\bibitem[\protect\citeauthoryear{??}{uml}{2005}]%
        {uml}
 \bibinfo{year}{2005}\natexlab{}.
\newblock \bibinfo{booktitle}{\emph{Unified Modeling Language:
  Superstructure}}.
\newblock \bibinfo{type}{{T}echnical {R}eport}. \bibinfo{institution}{Object
  Management Group}.
\newblock

\bibitem[\protect\citeauthoryear{??}{pmb}{2008}]%
        {pmbok4}
 \bibinfo{year}{2008}\natexlab{}.
\newblock \bibinfo{booktitle}{\emph{Project Management Body of Knowledge,
  Guide} (\bibinfo{edition}{4th} ed.)}.
\newblock \bibinfo{publisher}{Project Management Institute}.
\newblock

\bibitem[\protect\citeauthoryear{Bugayenko}{Bugayenko}{2016}]%
        {eo1}
\bibfield{author}{\bibinfo{person}{Yegor Bugayenko}.}
  \bibinfo{year}{2016}\natexlab{}.
\newblock \bibinfo{booktitle}{\emph{Elegant Objects}}.
  Vol.~\bibinfo{volume}{1}.
\newblock \bibinfo{publisher}{Amazon}.
\newblock

\bibitem[\protect\citeauthoryear{Chen}{Chen}{2009}]%
        {chen09}
\bibfield{author}{\bibinfo{person}{Betty~H.C. Chen}.}
  \bibinfo{year}{2009}\natexlab{}.
\newblock \showarticletitle{Current and Future Research Directions in
  Requirements Engineering}. In \bibinfo{booktitle}{\emph{Design Requirements
  Engineering: A Ten-Year Perspective In Design Requirements Engineering: A
  Ten-Year Perspective}}, Vol.~\bibinfo{volume}{14}. \bibinfo{pages}{11--43}.
\newblock

\bibitem[\protect\citeauthoryear{Clark, Harrison, Jenkins, Thompson, and
  Wo-jcik}{Clark et~al\mbox{.}}{2005}]%
        {clark05}
\bibfield{author}{\bibinfo{person}{P. Clark}, \bibinfo{person}{P. Harrison},
  \bibinfo{person}{T. Jenkins}, \bibinfo{person}{J. Thompson}, {and}
  \bibinfo{person}{R.~H. Wo-jcik}.} \bibinfo{year}{2005}\natexlab{}.
\newblock \showarticletitle{Acquiring and Using World Knowledge Using a
  Restricted Subset of English}. In \bibinfo{booktitle}{\emph{FLAIRS}}.
\newblock

\bibitem[\protect\citeauthoryear{Cockburn}{Cockburn}{2001}]%
        {cockburn01}
\bibfield{author}{\bibinfo{person}{Alistair Cockburn}.}
  \bibinfo{year}{2001}\natexlab{}.
\newblock \bibinfo{booktitle}{\emph{Writing Effective Use Cases}}.
\newblock \bibinfo{publisher}{Addison-Wesley}.
\newblock

\bibitem[\protect\citeauthoryear{Fuchs, Kaljurand, and Schneider}{Fuchs
  et~al\mbox{.}}{2006}]%
        {ace06}
\bibfield{author}{\bibinfo{person}{Norbert~E. Fuchs}, \bibinfo{person}{Kaarel
  Kaljurand}, {and} \bibinfo{person}{Gerold Schneider}.}
  \bibinfo{year}{2006}\natexlab{}.
\newblock \showarticletitle{{Attempto Controlled English Meets the Challenges
  of Knowledge Representation, Reasoning, Interoperability and User
  Interfaces}}. In \bibinfo{booktitle}{\emph{FLAIRS}}. Department of
  Informatics \& Institute of Computational Linguistics.
\newblock

\bibitem[\protect\citeauthoryear{IEEE}{IEEE}{1998}]%
        {ieee830}
\bibfield{author}{\bibinfo{person}{IEEE}.} \bibinfo{year}{1998}\natexlab{}.
\newblock \bibinfo{booktitle}{\emph{Recommended Practice for Software
  Requirements Specifications}}.
\newblock \bibinfo{type}{{T}echnical {R}eport} IEEE Std 830-1998.
  \bibinfo{institution}{The Institute of Electrical and Electronics Engineers}.
\newblock

\bibitem[\protect\citeauthoryear{Kof}{Kof}{2010}]%
        {kof10}
\bibfield{author}{\bibinfo{person}{L. Kof}.} \bibinfo{year}{2010}\natexlab{}.
\newblock \showarticletitle{From Requirements Documents to System Models: A
  Tool for Interactive Semi-Automatic Translation}. In
  \bibinfo{booktitle}{\emph{18th IEEE International Requirements Engineering
  Conference (RE)}}.
\newblock

\bibitem[\protect\citeauthoryear{Mavin, Wilkinson, Harwood, and Novak}{Mavin
  et~al\mbox{.}}{2009}]%
        {ears09}
\bibfield{author}{\bibinfo{person}{Alistair Mavin}, \bibinfo{person}{Philip
  Wilkinson}, \bibinfo{person}{Adrian Harwood}, {and} \bibinfo{person}{Mark
  Novak}.} \bibinfo{year}{2009}\natexlab{}.
\newblock \showarticletitle{{EARS (Easy Approach to Requirements Syntax)}}. In
  \bibinfo{booktitle}{\emph{17th IEEE International Requirements Engineering
  Conference ({RE})}}.
\newblock

\bibitem[\protect\citeauthoryear{Moynihan}{Moynihan}{2000}]%
        {moynihan00}
\bibfield{author}{\bibinfo{person}{Tony Moynihan}.}
  \bibinfo{year}{2000}\natexlab{}.
\newblock \showarticletitle{`Requirements-uncertainty': should it be a latent,
  aggregate or profile construct?}. In \bibinfo{booktitle}{\emph{Australian
  Software Engineering Conference}}. \bibinfo{pages}{181--188}.
\newblock

\bibitem[\protect\citeauthoryear{OMG}{OMG}{2011}]%
        {xmi}
\bibfield{author}{\bibinfo{person}{OMG}.} \bibinfo{year}{2011}\natexlab{}.
\newblock \bibinfo{booktitle}{\emph{{MOF} 2.0/{XMI} Mapping, Version 2.4.1}}.
\newblock \bibinfo{type}{{T}echnical {R}eport}. \bibinfo{institution}{Object
  Management Group}.
\newblock

\bibitem[\protect\citeauthoryear{Schwitter}{Schwitter}{[n.\,d.]}]%
        {peng}
\bibfield{author}{\bibinfo{person}{Rolf Schwitter}.}
  \bibinfo{year}{[n.\,d.]}\natexlab{}.
\newblock \bibinfo{title}{Processable {ENGlish}}.
\newblock
\newblock
\urldef\tempurl%
\url{http://web.science.mq.edu.au/~rolfs/peng/}
\showURL{%
\tempurl}

\bibitem[\protect\citeauthoryear{Sinha, Paradkar, Takeuchi, and Nakamura}{Sinha
  et~al\mbox{.}}{2010}]%
        {sinha10}
\bibfield{author}{\bibinfo{person}{A. Sinha}, \bibinfo{person}{A. Paradkar},
  \bibinfo{person}{H. Takeuchi}, {and} \bibinfo{person}{T. Nakamura}.}
  \bibinfo{year}{2010}\natexlab{}.
\newblock \showarticletitle{Extending Automated Analysis of Natural Language
  Use Cases to Other Languages}. In \bibinfo{booktitle}{\emph{18th IEEE
  International Requirements Engineering Conference (RE), 2010}}.
\newblock

\bibitem[\protect\citeauthoryear{West}{West}{2004}]%
        {west04}
\bibfield{author}{\bibinfo{person}{David West}.}
  \bibinfo{year}{2004}\natexlab{}.
\newblock \bibinfo{booktitle}{\emph{Object Thinking}}.
\newblock \bibinfo{publisher}{Microsoft Press}.
\newblock

\newpage

\bibitem[\protect\citeauthoryear{Wiegers}{Wiegers}{2003}]%
        {wiegers03}
\bibfield{author}{\bibinfo{person}{Karl Wiegers}.}
  \bibinfo{year}{2003}\natexlab{}.
\newblock \bibinfo{booktitle}{\emph{Software Requirements, Second Edition}}.
\newblock \bibinfo{publisher}{{Microsoft Press}}.
\newblock
\showISBNx{0735618798}

\bibitem[\protect\citeauthoryear{Woodcock and Davies}{Woodcock and
  Davies}{1996}]%
        {woodcock96}
\bibfield{author}{\bibinfo{person}{J. Woodcock} {and} \bibinfo{person}{J.
  Davies}.} \bibinfo{year}{1996}\natexlab{}.
\newblock \bibinfo{booktitle}{\emph{Using Z-Specification, Refinement and
  Proof}}.
\newblock \bibinfo{publisher}{Prentice Hall}.
\newblock

\end{thebibliography}
\bibliographystyle{ACM-Reference-Format}
